---
title: "Aula R Studio"
output: 
  ioslides_presentation:
    css: Estilo/styles.css
    logo: Imagens/logo.png
widescreen: true
author: Tiago Matos
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Introdução ao R {.flexbox .hcenter}

- R é uma linguagem de programação e ambiente de software para análise estatística, gráficos e relatórios. É amplamente utilizado nas áreas de estatística e ciência de dados


## Instalação e configuração

- Download do R: [CRAN](https://cran.r-project.org/)
- Download do Software: [RStudio](https://posit.co/downloads/)

## R Markdown {.build }

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure, echo=TRUE}
plot(pressure)
```

